\sffamily \Large Supplementary Information\\[0.1cm] {\bfseries Introspection dynamics in asymmetric multiplayers games}

### 2023-02-22 latex/article.tex
all figs done

\documentclass[11pt]{article}
\usepackage{times}
\usepackage{amsmath,amsthm,amssymb,bbold, mathtools,setspace,enumitem,epsfig,titlesec,verbatim,color,array,multirow,comment,graphicx,hyperref,blkarray}
%\usepackage[sort&compress]{natbib} % ProcB
\usepackage[super,sort&compress,comma]{natbib} % NComms
\usepackage[bf,small]{caption}
\usepackage[export]{adjustbox}
\usepackage[top=2.5cm,left=2.8cm,right=2.8cm,bottom=3.2cm]{geometry} 
\smallskip

@@

These frameworks have been applied to asymmetric games assuming co-evolving (finite) subpopulations of different player types. Fixation probabilities for asymmetric 2-player \cite{Sekiguchi:DGA:2017}, asymmetric 3-player games \cite{Sekiguchi:DGAA:2022}, and symmetric multiplayer games \cite{Kurokawa:PRSB:2009, gokhale:PNAS:2010} were recently derived. Whereas with intermediate mutation, strategy abundances were obtained only for 2-player asymmetric games \cite{Ohtsuki:JTB:2010, Sekiguchi:PA:2013} or multiplayer symmetric games \cite{gokhale:JTB:2011, Wu:Games:2013}. For a review on evolutionary multiplayer games both in infinitely large populations as well as in finite populations, we refer to \cite{Gokhale:DGAA:2014}.\\ 

@@

\newpage

@@

\noindent To compute the stationary distribution of introspection dynamics in a symmetric (general) public goods game (PG), we use the closed for expression in Eq. (\ref{Eq:stationary-dist-symm-2-stgs}). We consider that every player in a 4-player game can generate a benefit $b$ of value $2$. Before exploring the $c-w-N$ parameter space, we study four specific cases.  In two of these cases, the public goods is discounted ($w = 0.5$, Fig. \ref{Fig:GPGG-symmetric}a left panels) and in two other cases, the public goods is synergistic ($w = 1.5$, Fig. \ref{Fig:GPGG-symmetric}a right panels). For each case, we consider two sub-cases: one, in which cost is high ($c = 1$,  Fig. \ref{Fig:GPGG-symmetric}a top panels) and two, when cost is low ($c = 0.2$, Fig. \ref{Fig:GPGG-symmetric}a bottom panels). The four parameter combinations are chosen such that each of them represents a unique social dilemma under the replicator dynamics.  When the PG is discounted ($w = 0.5$) and costs are high ($c = 1$) defection dominates cooperation (the prisoner's dilemma). When the PG is discounted ($w = 0.5$) but costs are low ($c = 0.2$), the coexistence behaviour similar to the snowdrift game appears from the replicator equation. When the PG is synergistic ($w = 1.5$) and costs are high ($c = 1$), both cooperation and defection are locally stable equilibria. In addition, there is also an internal equilibrium which is unstable. This represents the stag-hunt game. And finally when both the PG is synergistic and costs are low, cooperation dominates defection. This situation represents the harmony game. The stationary behaviour of players in these games reflect the outcomes from the replicator dynamics (Fig. \ref{Fig:GPGG-symmetric}a). As selection strength is intermediate ($\beta = 5$), in some cases, players learn to play actions that are not optimal for the dilemma with non-zero probability. For example, even when the parameters of the game make cooperation to be the dominated strategy, there is a single cooperator in the group with a sizeable chance ($\approx 20\%$) in the long run. When the parameters of the game reflect the stag-hunt dilemma, players are more likely to coordinate their actions in the long run. In the long-run, the probabilities that the whole group plays $\C$ or $\D$ is higher than the probabilities that there is a group with a mixture of $\C$ and $\D$ players. In contrast, when the parameters reflect the snowdrift game, we get the opposite effect. In the long run, mixed groups are more likely than homogeneous groups. In fact, the group with exactly 2 cooperators and 2 defectors is the most likely outcome in the long run. Finally, when the parameters of the game make defection the dominated action, all players in the group learn to cooperate in the long run. \\ \\ 
\noindent The average cooperation frequency of the group in the long run are shown in the $c-w$ and $N-w$ parameter planes in Fig \ref{}b. First, let us consider the case when the group size is fixed at 4 players (the $c-w$ plane in Fig\ref{}b). In that case if the cost of cooperation is too high, the average cooperation rate is negligible and does not change with the change in the nature of the public good. When the cost is not restrictively high, the discount/synergy parameter, $w$, determines the frequency with which players cooperate in the long run. A high $w$ for the public good would result in high cooperation in the long run (and \emph{vice-versa}). Next we consider the case where the cost of cooperation is fixed (the $N-w$ plane in Fig. \ref{}b). It is fixed to a value such that in a synergistic PG ($w > 1$), the cooperation frequency is almost 1 in the long run for any group size. In this case, when the public good is discounted, group size $N$ and the discounting factor $w$ jointly determine the cooperation frequency in the long run. When the public good is discounted ($w < 1$), cooperation rates fall with larger group sizes. \\

@@

@@

\noindent Therefore, the stationary distribution sums up to 1. The candidate distribution we propose for the additive game is the unique stationary distribution of the process.

@@

When the above decomposition is perfomed $N-1$ more times, the sum of the right hand side becomes 1. This prooves that the candidate stationary distribution is also a probability distribution.

@@

\\ \noindent The final step in the previous simplification shows that Eq. (\ref{Eq:transition-in-proof}) holds for any $\abf \in \{\C,\D\}^N$. Therefore, the candidate distribution we propose in Eq. (\ref{Eq:stationary-dist-symm-2-stgs-state}) is the unique stationary distribution of the symmetric $N$-player game with two strategies. 

@@

\textbf{Symmetric linear public goods game.}
We use the following parameters for all the panels in this figure: $N = 4$ (group size), $b = 2$ (benefit provided to the public good on cooperation), $c = 1$ (cost of cooperation) a) Here we show the frequency of each state in the stationary distribution of introspection dynamics. As players are identical here, each state can be defined by the number of cooperators. We use a selection strength of $\beta = 5$ for the introspection dynamics. For this strength of selection, states with more cooperators are less likely than states with less cooperators in the stationary distribution b) The frequency of each state for varying selection strength, $\beta$. We use the same color code as the previous panel. Comparing neutrality ($\beta = 0$) with low to intermediate $\beta$ values, we see that selection favors states other than 0 cooperators. Indeed, up to $\beta \approx 3$, state $0$ is not the most frequent state in the long run c) Average cooperation frequency for varying dilemma strength depends on the selection strength $\beta$ and the parameters of the linear public goods game: $b,c, N$. We use the marginal gain of choosing cooperation over defection, $b/N - c$, as a measure of the dilemma strength. When this quantity is negative and low, we say that the dilemma is strong. In this case, there is no individual advantage to cooperate. When this quantity is positive and high, we say that the dilemma is weak. In this case, cooperation dominates defection. Typically, a linear public goods dilemma is defined to have a negative marginal gain (see conditions above). Here, we show the dilemma strength varying from $-2$ to $2$. The results are shown for different values of selection strength, $\beta = 1, 5$ and $100$. For high $\beta$, stationary distribution of the introspection dynamics reflects the rational play. In the long run player play the Nash equilibrium. When marginal gain is negative, defection is played with almost certainty (and \emph{vice-versa}). For low $\beta$, however, we see that some cooperation is possible even when the dilemma is strong. }

@@

\textbf{Asymmetric linear public goods game.} In the upper panels (a and b) we show the cost of cooperation and the benefit of provided due to cooperation for the three players on the left and the average cooperation frequency on the right. In this example, the cost of cooperation for players 1, 2 and 3 are $1 + \delta_c, 1$ and $1 - \delta_c$ respectively. The benefits that player 1, 2 and 3 provide upon cooperation are $2 + \delta_b, 2$ and $2 - \delta_b$ respectively. The cost and benefit for the reference player (player 2) are shown with black dashed lines in the left panels of a and b. In a) player 1 and 3 differ by 0.5 units in their cost of cooperation from the reference player. All the players provide the same benefit when they contribute (i.e., $\delta_b = 0$). Conversely, in b) benefit by player 1 and 3 differ from the reference player by 1 unit. The cost of cooperation is the same for all players ($c = 1$). In c), we vary the asymmetry strengths $\delta_c $ and $\delta_b$ simultaneously and show both average individual cooperation frequency and the overall average cooperation frequency in the long-run. The reference player's cost and benefit are 1 and 2 units respectively. The area within the white dashed lines represents the parameter values for which the marginal gain of choosing cooperation over defection is negative, for each single player and, in the right-most panel, for all players simultaneously. For panels a and b we use a selection strength of $\beta = 2$ while for panel c, we use a selection strength of $\beta = 5$. 

@@

\includegraphics[width =  0.65\textwidth, keepaspectratio]{figures/figure3}~\\[0.4cm]

@@

\textbf{Symmetric general public goods game}. We study introspection dynamics in the general public goods game with 4 symmetric players, each having two possible actions - cooperation and defection. For a detailed description of the game, please see the main text. a) The frequency of each state in the stationary distribution of introspection dynamics in four types of multiplayer social dilemmas display qualitatively different results. The upper panels refer to a high cost of cooperation ($c=1$) while the bottom panels to a low cost of cooperation ($c = 0.2$); left panels refer to a discounted public good ($w = 0.5$), and the right panels refer to a synergistic public good ($w = 1.5$). Each case is tagged with a symbol that places the particular case in the contour plot in panel b, b) Average cooperation frequency for varying discount/synergy factor, $w$, and varying cost of cooperation, $c$. Cooperation is feasible when costs are not restrictively high and the public good is not too discounted. c) Average cooperation frequency for varying discount/synergy factor, $w$, and group size $N$. For this plot,the cost of cooperation for each player is $c = 0.4$. The feasibility of cooperation drops with larger group sizes when the public good is discounted. For all panels, the benefit of cooperation generated by each player is worth 2 units. The selection strength of the process is $\beta = 5$ for all panels.} 

@@

\textbf{Cooperation and social rewarding in the stationary distribution of introspection dynamics in the linear public goods game with peer rewarding} Here we study a game with three asymmetric players, each having 16 possible strategies. Players cooperate in a linear public goods and then reward each other in the next stage after everyone's contribution is revealed. Players can condition their cooperation on the information they have about their co-players' rewarding strategies. For a full description of the model, please see the section on rewarding above. In this example, players 1 and 2 are identical in all aspects while player 3 is asymmetric to them in only a single aspect. In here, we plot the average frequency with which players cooperate and reward cooperation after a long time (after $10^5$ time steps of a computer simulation). We consider three types of asymmetry for player 3. a) First, we consider the case where player 3 has a high cost of rewarding compared to player 1 and 2, $0.7 = \gamma_3 > \gamma_1 = 0.1$. b) Then, we consider the case where player 3 is less productive than their co-players, $1.2 = r_3 < r_1 = 2$. c) Finally, we consider the case where player 3 has less information about co-players' rewarding strategies than their peers, that is, $0.1 = \lambda_3 < \lambda_1 = 0.9$. For all plots, we consider the selection strength of players are high, $\beta = 10$. Unless otherwise mentioned, the following parameters are maintained for all panels: $c_i = 1$ (individual cost of cooperation), $r_i = 2$ (individual productivity), $\gamma_i = 0.1$ (individual cost of cooperation), $\lambda_i = 0.9$ (individual information about co-players' strategies). In panels a and b, the reward value $\rho$ is 0.3 while for the last panel, c, the reward value $\rho = 1$.}

>>>>

\documentclass[11pt]{article}
\usepackage{times}
\usepackage{amsmath,amsthm,amssymb,bbold, mathtools,setspace,enumitem,epsfig,titlesec,verbatim,color,array,multirow,comment,graphicx,hyperref,blkarray}
\usepackage[sort&compress]{natbib} % ProcB
%\usepackage[super,sort&compress,comma]{natbib} % NComms
\usepackage[bf,small]{caption}
\usepackage[export]{adjustbox}
\usepackage[top=2.5cm,left=2.8cm,right=2.8cm,bottom=3.2cm]{geometry} 
\smallskip

@@

These frameworks have been applied to asymmetric games assuming co-evolving (finite) subpopulations of different player types. Fixation probabilities for asymmetric 2-player \cite{Sekiguchi:DGA:2017}, asymmetric 3-player games \cite{Sekiguchi:DGAA:2022}, and symmetric multiplayer games \cite{Kurokawa:PRSB:2009, gokhale:PNAS:2010} were recently derived. Whereas with intermediate mutation, strategy abundances were obtained only for 2-player asymmetric games \cite{Ohtsuki:JTB:2010, Sekiguchi:PA:2013} or multiplayer symmetric games \cite{gokhale:JTB:2011, Wu:Games:2013, Kroumi:Jmb:2022}. For a review on evolutionary multiplayer games both in infinitely large populations as well as in finite populations, we refer to \cite{Gokhale:DGAA:2014}.\\ 

@@

@@

\noindent To compute the stationary distribution of introspection dynamics in a symmetric (general) public goods game (PG), we use the closed for expression in Eq. (\ref{Eq:stationary-dist-symm-2-stgs}). We consider that every player in a 4-player game can generate a benefit $b$ of value $2$. Before exploring the $c-w-N$ parameter space, we study four specific cases.  In two of these cases, the public goods is discounted ($w = 0.5$, Fig. \ref{Fig:GPGG-symmetric}a left panels) and in two other cases, the public goods is synergistic ($w = 1.5$, Fig. \ref{Fig:GPGG-symmetric}a right panels). For each case, we consider two sub-cases: one, in which cost is high ($c = 1$,  Fig. \ref{Fig:GPGG-symmetric}a top panels) and two, when cost is low ($c = 0.2$, Fig. \ref{Fig:GPGG-symmetric}a bottom panels). The four parameter combinations are chosen such that each of them represents a unique social dilemma under the replicator dynamics.  When the PG is discounted ($w = 0.5$) and costs are high ($c = 1$) defection dominates cooperation (the prisoner's dilemma). When the PG is discounted ($w = 0.5$) but costs are low ($c = 0.2$), the coexistence behaviour similar to the snowdrift game appears from the replicator equation. When the PG is synergistic ($w = 1.5$) and costs are high ($c = 1$), both cooperation and defection are locally stable equilibria. In addition, there is also an internal equilibrium which is unstable. This represents the stag-hunt game. And finally when both the PG is synergistic and costs are low, cooperation dominates defection. This situation represents the harmony game. The stationary behaviour of players in these games reflect the outcomes from the replicator dynamics (Fig. \ref{Fig:GPGG-symmetric}a). As selection strength is intermediate ($\beta = 5$), in some cases, players learn to play actions that are not optimal for the dilemma with non-zero probability. For example, even when the parameters of the game make cooperation to be the dominated strategy, there is a single cooperator in the group with a sizeable chance ($\approx 20\%$) in the long run. When the parameters of the game reflect the stag-hunt dilemma, players are more likely to coordinate their actions in the long run. In the long-run, the probabilities that the whole group plays $\C$ or $\D$ is higher than the probabilities that there is a group with a mixture of $\C$ and $\D$ players. In contrast, when the parameters reflect the snowdrift game, we get the opposite effect. In the long run, mixed groups are more likely than homogeneous groups. In fact, the group with exactly 2 cooperators and 2 defectors is the most likely outcome in the long run. Finally, when the parameters of the game make defection the dominated action, all players in the group learn to cooperate in the long run. \\ \\ 
\noindent The average cooperation frequency of the group in the long run are shown in the $c-w$ and $N-w$ parameter planes in Fig \ref{Fig:GPGG-symmetric}b. First, let us consider the case when the group size is fixed at 4 players (the $c-w$ plane in Fig\ref{Fig:GPGG-symmetric}b). In that case if the cost of cooperation is too high, the average cooperation rate is negligible and does not change with the change in the nature of the public good. When the cost is not restrictively high, the discount/synergy parameter, $w$, determines the frequency with which players cooperate in the long run. A high $w$ for the public good would result in high cooperation in the long run (and \emph{vice-versa}). Next we consider the case where the cost of cooperation is fixed (the $N-w$ plane in Fig. \ref{}b). It is fixed to a value such that in a synergistic PG ($w > 1$), the cooperation frequency is almost 1 in the long run for any group size. In this case, when the public good is discounted, group size $N$ and the discounting factor $w$ jointly determine the cooperation frequency in the long run. When the public good is discounted ($w < 1$), cooperation rates fall with larger group sizes.\\ 

@@

We also study the introspection dynamics in general public goods game with asymmetric players. We use the same setup that we used for studying the linear public goods with three asymmetric players. The average frequency of cooperation per player is summarized in Supplementary Figures 1 and 2. First, we study two cases, one in which the public good is synergized (and players have a high average cost) and two in which public good is discounted (and players have a lower average cost). In the first case, the player with the highest benefit cooperates only when they have a low cost of cooperation. 

@@

\noindent Therefore, the stationary distribution sums up to 1. The candidate distribution we propose for the additive game is the unique stationary distribution of the process.\\

@@

When the above decomposition is perfomed $N-1$ more times, the sum of the right hand side becomes 1. This prooves that the candidate stationary distribution is also a probability distribution.\\

@@

\\ \noindent The final step in the previous simplification shows that Eq. (\ref{Eq:transition-in-proof}) holds for any $\abf \in \{\C,\D\}^N$. Therefore, the candidate distribution we propose in Eq. (\ref{Eq:stationary-dist-symm-2-stgs-state}) is the unique stationary distribution of the symmetric $N$-player game with two strategies. \\

@@

\textbf{Introspection dynamics in a symmetric linear public goods game.}
The stationary distribution of the introspection dynamics for a linear public goods game with all identical players is shown in this figure. For all the panels in this figure, we use the following parameters: $N = 4$ (group size), $b = 2$ (benefit provided to the public good upon cooperation), $c = 1$ (cost of cooperation) a) Here we show the frequency of each state in the stationary distribution of introspection dynamics. As players are identical, each state can be defined by the number of cooperators. We use a selection strength of $\beta = 5$ for the introspection dynamics. For this strength of selection, states with more cooperators are less likely than states with less cooperators in the stationary distribution b) Here we show the frequency of each state for varying selection strength, $\beta$. We use the same color code as the previous panel. Comparing neutrality ($\beta = 0$) with low to intermediate $\beta$ values, we see that selection favors states other than 0 cooperators. Indeed, up to $\beta \approx 3$, state $0$ is not the most frequent state in the long run. c) Average cooperation frequency for varying dilemma strength depends on the selection strength, $\beta$, and the parameters of the linear public goods game: $b,c, N$. We use the marginal gain of choosing cooperation over defection, $b/N - c$, as a measure of the dilemma strength. When this quantity is negative and low, we say that the dilemma is strong. In this case, chosing cooperation is strictly disadvantageous. When this quantity is positive and high, we say that the dilemma is weak. In this case, cooperation dominates defection. Typically, a linear public goods dilemma is defined to have a negative marginal gain. Here, we show the dilemma strength varying from $-2$ to $2$. The results are shown for different values of selection strength, $\beta = 1, 5$ and $100$. For high $\beta$, stationary distribution of the introspection dynamics reflects the rational play. In the long-run player play the Nash equilibrium. When marginal gain is negative, defection is played with almost certainty (and \emph{vice-versa}). For low $\beta$, however, we see that some cooperation is possible even when the dilemma is strong. }

@@

\textbf{Introspection dynamics in an asymmetric linear public goods game.} Three asymmetric players learn to play the linear public goods game through introspection dynamics. The cooperation probabilities in the stationary distribution are displayed here. For each of the upper panels (a and b), we show the cost of cooperation and the benefit provided upon cooperation for the players on the left and the average cooperation frequency in the long-run on the right. In this example, the cost of cooperation for players 1, 2 and 3 are $1 + \delta_c, 1$ and $1 - \delta_c$ respectively. The benefits that player 1, 2 and 3 provide upon cooperation are $2 + \delta_b, 2$ and $2 - \delta_b$ respectively. The cost and benefit for the reference player (player 2) are shown with black dashed lines in the left panels of a and b. In panel a, player 1 and 3 differ by 0.5 units in their cost of cooperation from the reference player. All the players provide the same benefit when they contribute (i.e., $\delta_b = 0$). Conversely, in panel b, benefit by player 1 and 3 differ from the reference player by 1 unit. The cost of cooperation is the same for all players ($c = 1$). In c), we vary the asymmetry strengths between the players, $\delta_c $ and $\delta_b$, simultaneously and show both average individual cooperation frequency and the overall average cooperation frequency in the long-run. The reference player's cost and benefit are again 1 and 2 units respectively. The area within the white dashed lines represents the parameter values for which the marginal gain of choosing cooperation over defection is negative, for each single player and, in the right-most panel, for all players simultaneously. In this example, with this specific asymmetrical players, cooperation is only feasible in the long run if the asymmetries of players are aligned. That is, overall cooperation is high only when the individual with a low cost of cooperation has a high benefit value. For panels a and b we use a selection strength of $\beta = 2$ while for panel c, we use a selection strength of $\beta = 5$. 

@@

\includegraphics[width =  0.65\textwidth, keepaspectratio]{figures/figure3.eps}~\\[0.4cm]

@@

\textbf{Introspection dynamics in a symmetric general public goods game}. We study introspection dynamics in the general public goods game with 4 symmetric players, each having two possible actions - cooperation and defection. For a detailed description of the game, please see the main text. a) The frequency of each state in the stationary distribution of introspection dynamics in four types of multiplayer social dilemmas display qualitatively different results. The upper panels refer to a high cost of cooperation ($c=1$) while the bottom panels to a low cost of cooperation ($c = 0.2$); left panels refer to a discounted public good ($w = 0.5$), and the right panels refer to a synergistic public good ($w = 1.5$). Each case is tagged with a symbol that places the particular case in the contour plot in panel b, b) Average cooperation frequency for varying discount/synergy factor, $w$, and varying cost of cooperation, $c$. Cooperation is feasible when costs are not restrictively high and the public good is not too discounted. c) Here we show the average cooperation frequency for varying discount/synergy factor, $w$, and group size $N$. For this plot, the cost of cooperation for each player is $c = 0.4$. The feasibility of cooperation drops with larger group sizes when the public good is discounted. For all panels, the benefit of cooperation generated by each player is worth 2 units. The selection strength of the introspection dynamics is $\beta = 5$ for all panels.} 

@@

\textbf{Intropection dynamics in a game with linear public goods game with peer rewarding.} Here we study a game with three asymmetric players, each having 16 possible strategies. Players cooperate in a linear public goods and then reward each other in the next stage after everyone's contribution is revealed. In the first stage, players can condition their cooperation on the information they have about their co-players' rewarding strategies. For a full description of the model, please see the section on rewarding. In this example, players 1 and 2 are identical in all aspects while player 3 is asymmetric to them in only a single aspect. In here, we plot the average frequency with which players cooperate and reward cooperation after a long time (after $10^5$ time steps of a computer simulation). We consider three types of asymmetry for player 3. a) First, we consider the case where player 3 has a high cost of rewarding compared to player 1 and 2, $0.7 = \gamma_3 > \gamma_1 = 0.1$. b) Then, we consider the case where player 3 is less productive than their co-players, $1.2 = r_3 < r_1 = 2$. c) Finally, we consider the case where player 3 has less information about co-players' rewarding strategies than their peers, that is, $0.1 = \lambda_3 < \lambda_1 = 0.9$. For all plots, we consider a high value for the selection strenght, $\beta = 10$. Unless otherwise mentioned, the following parameters are maintained for all panels: $c_i = 1$ (individual cost of cooperation), $r_i = 2$ (individual productivity), $\gamma_i = 0.1$ (individual cost of rewarding), $\lambda_i = 0.9$ (individual information about co-players' strategies). In panels a and b, the reward value $\rho$ is 0.3 while for the last panel, c, the reward value $\rho = 1$.}

### 2023-02-22 latex/supp.tex
all figs done

\begin{document}
\maketitle
\onehalfspacing
\section*{Supplementary Figures}
\begin{figure}[h!]
\centering
\includegraphics[width =  \textwidth]{figures/figure1.eps}~\\[0.4cm]
\caption{\onehalfspacing
\textbf{Symmetric linear public goods game.}
a) Frequency of each state in the stationary distribution of introspection dynamics. As players are indistinguishable here, each state can be fully defined by the number of cooperators. Parameters: $N = 4$, $b = 2$, $c = 1$ and $\beta = 5$. b) For the same game parameters ($N = 4$, $b = 2$ and $c = 1$), we now show the frequency of each state (same color code as in panel a) for varying selection strength $\beta$. Comparing neutrality ($\beta = 0$) with low to intermediate $\beta$ values, we see that selection favors states other than 0 cooperators. Indeed, up to $\beta \approx 3$, state $0$ is not even the most frequent. c) Average cooperation frequency for varying dilemma strength. We use as a measure of the dilemma strength the marginal gain by choosing to cooperate over choosing to defect, $b/N - c$. When this quantity is low, we say there is a ``strong dilemma”, where there is no individual advantage to cooperate, whereas when the marginal gain is high, we say there is a ``weak dilemma” (or no dilemma), where to cooperate becomes advantageous. Typically, a linear public goods dilemma is defined as having a negative marginal gain (see conditions above). Here, we show the whole parameter range for completeness and a full grasp of this game. We also show the result for different values of selection strength, $\beta = 1, 5$ and $100$. For high $\beta$, we confirm the classical prediction that, assuming a negative marginal gain, defection is dominant. For low $\beta$, however, we see again that some cooperation is possible. }
\label{Fig:LPGG-symmetric}
\end{figure}
\clearpage

\begin{figure}
\centering
\includegraphics[width =  \textwidth]{figures/figure2.eps}~\\[0.4cm]
\caption{\onehalfspacing
\textbf{Asymmetric linear public goods game.} In the upper panels a) and b), we show the parameter values of the cost and benefit on the left and the average cooperation frequency on the right, of each player. Parameters: $N=3$, $\bar{c} = 1$, $\bar{b} = 2$, $\beta = 2$, where $\bar{c}$ and $\bar{b}$ are the mean values and are represented by black, dashed lines. In a) the cost varies among the 3 players by $\delta_c = 0.5$, such that players have costs of $\bar{c} + \delta_c $, $\bar{c}$, and $\bar{c} - \delta_c$ (in this case, $1.5$, $1$, and $0.5$), while the benefit is the same. Conversely, in b) the benefit varies among the 3 players, by $\delta_b = 1$, such that players have benefits of $\bar{b} + \delta_b $, $\bar{b}$, and $\bar{b} - \delta_b$ (in this case, $3$, $2$, and $1$), while the cost is the same. In c), we vary the asymmetry strengths $\delta_c $ and $\delta_b$ at the same time and show both each player’s average cooperation frequency and the overall average cooperation frequency. The area within the white dashed lines represents the parameter range for which the marginal gain by cooperating is negative, for each single player and, in the right-most panel, for all players. Parameters: $N=3$, $\bar{c} = 1$, $\bar{b} = 2$, $\beta = 5$.
}
\label{Fig:LPGG-asymmetric}
\end{figure}
\end{document}

>>>>

\begin{document}
\maketitle
\onehalfspacing
\section*{Supplementary Figures: Asymmetric general public goods game}

\begin{figure}[h!]
\centering
\includegraphics[width =  \textwidth]{figures/Supfigure1.eps}~\\[0.4cm]
\caption{\onehalfspacing
\textbf{Introspection dynamics in general public goods game with asymmetric players. We show stationary properties of the dynamics in a game with particular values of synergy/discount parameter and reference cost.} For a detailed description of the game, please see the section on general public goods game the main text. The setup is the same as Figure 3 of main text. There are three players with asymmetric costs and benefits. The respective costs for player 1, 2 and 3 are $c + \delta_c, c$, and $c - \delta_c$ respectively. The respective benefits they provide upon cooperation are $b + \delta_b, b$ and $b - \delta_b$ respectively. The parameters $c$ and $b$ respectively are the cost and benefits of the reference player (player 2). In here, we look at the cooperation probability for each player (and also overall cooperation) in stationary distribution of the introspection process. Players use a selection strength of $\beta = 5$. In the top row, we i) set the public good to be synergistic $w = 1.5$ and ii) allow a high reference cost, $c = 1$. In the bottom row, we i) set the public good to be discounted $w = 0.5$ and ii) allow a low reference cost $c = 0.2$. }

\label{Fig:Supp-Fig1}
\end{figure}
\clearpage

\begin{figure}
\centering
\includegraphics[width =  \textwidth]{figures/Supfigure2.eps}~\\[0.4cm]
\caption{\onehalfspacing
\textbf{Introspection dynamics in general public goods game with asymmetric players. We show stationary properties of the dynamics in a game with fixed asymmetry strengths.} For a detailed description of the game, please see the section on general public goods game in the main text. The setup is the same as Supplementary Figure \ref{Fig:Supp-Fig1}. In here, we show the cooperation probability of each player (and also the overall cooperation) in the stationary distribution of the introspection process versus the reference cost $c$ (cost of player 2) and tthe synergy/discount factor of the public good, $w$. For each row, the strength of asymmetry between the players is fixed. In the top row, the players do not differ in their benefits (they all have a benefit of value 2) but player 1 and player 3 have their cost of cooperation 0.5 units higher and lower respectively than player 2 (cost of cooperation for player 2 is varied in the y-axis). In the bottom row, all the players have the same cost of cooperation, $c$ (which is varied in the y-axis). In this case, player 1, 2 and 3 generate asymmetric benefits. Player 1,2 and 3 generate, 3, 2 and 1 units of benefits. 
}
\label{Fig:Supp-Fig2}
\end{figure}
\end{document}
